---
title: "DE analyses PROJ0000003_DEEXPRNA"
author: "Andrew Li Yim"
date: "November 9, 2016"
output: pdf_document
---

In this workbook we will perform differential expression analysis on human ileal fibroblasts that were extracted from resection material and cultured. We are interested in finding the genes that are differentially expressed among the different groups:
- CD vs Non-CD
- INF vs NINF
- STEN vs NINF

```{r setup}
data_dir <- file.path("data/02_gene_expression")
output_dir <- file.path("output/02_gene_expression")

top_dir <- file.path(output_dir, "top_genes")
dir.create(top_dir)

#Colorblind color palette
cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
```

Import the DESeqDataset
```{r Import dds}
dds_intraCD <- readRDS(file.path(output_dir, "preprocessing", "dds_intraCD.Rds"))
dds_interCD <- readRDS(file.path(output_dir, "preprocessing", "dds_interCD.Rds"))
```

Perform DESeq analyses
```{r DESeq}
dds_intraCD <- DESeq(dds_intraCD)
dds_interCD <- DESeq(dds_interCD)

rld <- assay(rlog(dds_intraCD, blind = F))
```

We now perform pairwise Wald tests:
```{r CD vs Non_CD}
require(NDlib)

results_CDvNon_CD <- results(dds_interCD, contrast=c("Phenotype", "CD", "Non_CD"))
results_CDvNon_CD <- results_CDvNon_CD[order(results_CDvNon_CD$pvalue),]
results_CDvNon_CD$hgnc_symbol <- rowData(dds_interCD)[match(rownames(results_CDvNon_CD), rowData(dds_interCD)$ensembl_gene_id), "hgnc_symbol"]
results_CDvNon_CD$entrez_id <- rowData(dds_interCD)[match(rownames(results_CDvNon_CD), rowData(dds_interCD)$ensembl_gene_id), "entrezgene"]
if(length(which(is.na(results_CDvNon_CD$padj))) != 0){
  results_CDvNon_CD <- results_CDvNon_CD[-which(is.na(results_CDvNon_CD$padj)),]  
}

CDvNon_CD_dir <- file.path(top_dir, "CDvNon_CD")
dir.create(CDvNon_CD_dir)

write.csv(results_CDvNon_CD, file = file.path(CDvNon_CD_dir, "DEGs_CDvNon_CD.csv"))

#GSEA
rnk_CDvNon_CD <- data.frame(results_CDvNon_CD$entrez_id, results_CDvNon_CD$stat)
rnk_CDvNon_CD <- rnk_CDvNon_CD[!is.na(rnk_CDvNon_CD$results_CDvNon_CD.entrez_id),]
write.table(rnk_CDvNon_CD, file = file.path(CDvNon_CD_dir, "CDvNon_CD.rnk"), quote = F, row.names = F, col.names = F)

#Plotting
require(Cairo)
for(i in 1:10){
  #Cairo(file = file.path(CDvNon_CD_dir, paste0(i, "_", rownames(results_CDvNon_CD)[i], "_", results_CDvNon_CD$hgnc_symbol[i], ".pdf")), type = "pdf", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
  print(transcript_strip_plot(id = rownames(results_CDvNon_CD)[i], 
                              type = "SE",
                              counts = rld, 
                              y_lab = "log2(counts)", 
                              title = results_CDvNon_CD$hgnc_symbol[i],
                              factor_interest = colData(dds_interCD)$Phenotype))
  #dev.off()
}

Cairo(file = file.path(CDvNon_CD_dir, "CDvNon_CD_volcano.png"), type = "png", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
volcano_plot(effect_sizes = results_CDvNon_CD$log2FoldChange, 
             title = "CD vs Non_CD",
             pvals = results_CDvNon_CD$pvalue, 
             significance = results_CDvNon_CD$padj < 0.05, 
             identifiers = results_CDvNon_CD$hgnc_symbol, 
             int_effect_threshold = 1, 
             top_names = 10)
dev.off()
```

```{r INF vs NINF}
require(NDlib)

results_INFvNINF <- results(dds_intraCD, contrast=c("Degree", "INF", "NINF"))
results_INFvNINF <- results_INFvNINF[order(results_INFvNINF$pvalue),]
results_INFvNINF$hgnc_symbol <- rowData(dds_intraCD)[match(rownames(results_INFvNINF), rowData(dds_intraCD)$ensembl_gene_id), "hgnc_symbol"]
results_INFvNINF$entrez_id <- rowData(dds_intraCD)[match(rownames(results_INFvNINF), rowData(dds_intraCD)$ensembl_gene_id), "entrezgene"]
if(length(which(is.na(results_INFvNINF$padj))) != 0){
  results_INFvNINF <- results_INFvNINF[-which(is.na(results_INFvNINF$padj)),]  
}

INFvNINF_dir <- file.path(top_dir, "INFvNINF")
dir.create(INFvNINF_dir)

write.csv(results_INFvNINF, file = file.path(INFvNINF_dir, "DEGs_INFvNINF.csv"))

#GSEA
rnk_INFvNINF <- data.frame(results_INFvNINF$entrez_id, results_INFvNINF$stat)
rnk_INFvNINF <- rnk_INFvNINF[!is.na(rnk_INFvNINF$results_INFvNINF.entrez_id),]
write.table(rnk_INFvNINF, file = file.path(INFvNINF_dir, "INFvNINF.rnk"), quote = F, row.names = F, col.names = F)

#Plotting
require(Cairo)
for(i in 1:10){
  Cairo(file = file.path(INFvNINF_dir, paste0(i, "_", rownames(results_INFvNINF)[i], "_", results_INFvNINF$hgnc_symbol[i], ".pdf")), type = "pdf", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
  print(transcript_strip_plot(id = rownames(results_INFvNINF)[i], 
                              type = "SE",
                              counts = rld, 
                              y_lab = "log2(counts)", 
                              title = results_INFvNINF$hgnc_symbol[i],
                              factor_interest = colData(dds_interCD)$Degree))
  dev.off()
}

Cairo(file = file.path(INFvNINF_dir, "INFvNINF_volcano.png"), type = "png", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
volcano_plot(effect_sizes = results_INFvNINF$log2FoldChange, 
             title = "INF vs NINF",
             pvals = results_INFvNINF$pvalue, 
             significance = results_INFvNINF$padj < 0.05, 
             identifiers = results_INFvNINF$hgnc_symbol, 
             int_effect_threshold = 1, 
             top_names = 10)
dev.off()
```

```{r STEN vs NINF}
require(NDlib)

results_STENvNINF <- results(dds_intraCD, contrast=c("Degree", "STEN", "NINF"))
results_STENvNINF <- results_STENvNINF[order(results_STENvNINF$pvalue),]
results_STENvNINF$hgnc_symbol <- rowData(dds_intraCD)[match(rownames(results_STENvNINF), rowData(dds_intraCD)$ensembl_gene_id), "hgnc_symbol"]
results_STENvNINF$entrez_id <- rowData(dds_intraCD)[match(rownames(results_STENvNINF), rowData(dds_intraCD)$ensembl_gene_id), "entrezgene"]
if(length(which(is.na(results_STENvNINF$padj))) != 0){
  results_STENvNINF <- results_STENvNINF[-which(is.na(results_STENvNINF$padj)),]  
}

STENvNINF_dir <- file.path(top_dir, "STENvNINF")
dir.create(STENvNINF_dir)

write.csv(results_STENvNINF, file = file.path(STENvNINF_dir, "DEGs_STENvNINF.csv"))

#GSEA
rnk_STENvNINF <- data.frame(results_STENvNINF$entrez_id, results_STENvNINF$stat)
rnk_STENvNINF <- rnk_STENvNINF[!is.na(rnk_STENvNINF$results_STENvNINF.entrez_id),]
write.table(rnk_STENvNINF, file = file.path(STENvNINF_dir, "STENvNINF.rnk"), quote = F, row.names = F, col.names = F)

#Plotting
require(Cairo)
for(i in 1:10){
  Cairo(file = file.path(STENvNINF_dir, paste0(i, "_", rownames(results_STENvNINF)[i], "_", results_STENvNINF$hgnc_symbol[i], ".pdf")), type = "pdf", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
  print(transcript_strip_plot(id = rownames(results_STENvNINF)[i], 
                              type = "SE",
                              counts = rld, 
                              y_lab = "log2(counts)", 
                              title = results_STENvNINF$hgnc_symbol[i],
                              factor_interest = colData(dds_interCD)$Degree))
  dev.off()
}

Cairo(file = file.path(STENvNINF_dir, "STENvNINF_volcano.png"), type = "png", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
volcano_plot(effect_sizes = results_STENvNINF$log2FoldChange, 
             title = "STEN vs NINF",
             pvals = results_STENvNINF$pvalue, 
             significance = results_STENvNINF$padj < 0.05, 
             identifiers = results_STENvNINF$hgnc_symbol, 
             int_effect_threshold = 1, 
             top_names = 10)
dev.off()
```

```{r Combined volcano plot}
CDvNon_CD_sub <- cbind(data.frame(results_CDvNon_CD[,c("log2FoldChange", "pvalue", "padj", "hgnc_symbol")]), Comparison = "CDvNon_CD")
INFvNINF_sub <- cbind(data.frame(results_INFvNINF[,c("log2FoldChange", "pvalue", "padj", "hgnc_symbol")]), Comparison = "INFvNINF")
STENvNINF_sub <- cbind(data.frame(results_STENvNINF[,c("log2FoldChange", "pvalue", "padj", "hgnc_symbol")]), Comparison = "STENvNINF")

results_sub <- rbind(CDvNon_CD_sub, INFvNINF_sub, STENvNINF_sub)
colnames(results_sub) <- c("logfc", "pvalue", "padj", "hgnc_symbol", "comparison")
results_sub$significant <- ifelse(results_sub$padj < 0.05, 1, 0.1)
results_sub$logpval <- -log10(results_sub$pvalue)

ggplot(results_sub, aes(x = logfc, y = logpval, col = comparison, alpha = significant)) +
  geom_point() +
  theme_bw()

```
This does not look as good as I envisioned it.

```{r Enrichment analyses}
pathway_enrichplot <- function(results, n = 10){
  pathwayid <- gsub("Homo sapiens: ", "", rownames(results))
  pathwayid <- gsub("^(.+?) (.+)$", "(\\1) \\2", pathwayid)
  pathwayid_wrapped <- sapply(X = pathwayid, FUN = function(x){
    paste(strwrap(x,width=20), collapse="\n")
  }, simplify = T)
  results$pathwayid <- pathwayid_wrapped
  
  data_df <- head(results, n = n)

  plot_df <- data.frame(pathway = data_df$pathwayid,
                        logpval = -log10(data_df$PValue),
                        Significant = factor(ifelse(data_df$FDR < 0.05, T, F), levels = c(T, F)))

  ggplot(plot_df, aes(x = pathway, y = logpval)) +
    geom_point(aes(col = Significant)) +
    scale_x_discrete(limits=rev(plot_df$pathway)) +
    theme_bw() +
    ylab("-log10(p)") +
    theme(axis.title.y=element_blank(),
          axis.ticks.y=element_blank(),
          axis.title.x = element_text(size = 14, face = "bold"),
          axis.text.x = element_text(size = 12), 
          legend.title = element_text(size = 14, face = "bold"),
          legend.text = element_text(size = 12)) +
    scale_colour_hue(drop = FALSE) +
    coord_flip() +
    ylim(0, NA)
}


require(limma)
msigdb_dir <- file.path("~/hdd1/common_data/MSigDb")
msigdb_c2 <- scan(file.path(msigdb_dir, "c2.all.v6.1.entrez.gmt"), what="", sep="\n")
msigdb_c2 <- strsplit(msigdb_c2, "[[:space:]]+")
names(msigdb_c2) <- sapply(msigdb_c2, `[[`, 1)
msigdb_c2 <- lapply(msigdb_c2, `[`, -c(1:2))
saveRDS(msigdb_c2, file.path(msigdb_dir, "c2.all.v6.1.entrez.Rds"))

#I only take the KEGG and reactome pathways as the others often include disease specific gene sets, which are at the moment less interesting
msigdb_c2_kegg_reactome <- msigdb_c2[grep("(REACTOME|KEGG)", names(msigdb_c2))]

design_matrix_inter <- model.matrix(~0 + Phenotype + Passage + Gender + Age + Medication, data = colData(dds_interCD))
#design_matrix_inter <- model.matrix(~Phenotype, data = colData(dds_interCD))
design_matrix_intra <- model.matrix(~0 + Degree + Passage + Gender + Age + Medication, data = colData(dds_intraCD))
#design_matrix_intra <- model.matrix(~0 + Degree, data = colData(dds_intraCD))

contrast_matrix_interCD <- makeContrasts(
  CDvNon_CD = PhenotypeCD-PhenotypeNon_CD,
  levels = design_matrix_inter
)

contrast_matrix_intraCD <- makeContrasts(
  INFvNINF = DegreeINF-DegreeNINF,
  STENvNINF = DegreeSTEN-DegreeNINF,
  levels = design_matrix_intra
)

rld_entrez <- rld
rownames(rld_entrez) <- rowData(dds_intraCD)$entrezgene
rld_entrez <- rld_entrez[!is.na(rownames(rld_entrez)),]

#Databases
require(reactome.db)
require(gage)

kegg_set <- kegg.gsets("hsa")$kg.sets
reactome_set <- as.list(reactomePATHID2EXTID)
reactome_set <- reactome_set[grep("HSA", names(reactome_set))]
reactome_names <- as.list(reactomePATHID2NAME)

names(reactome_set) <- paste0(names(reactome_set), " ", unlist(reactome_names)[names(reactome_set)])

geneset <- c(reactome_set, kegg_set)

CDvNon_CD_camera_c2 <- camera(rld_entrez, index = geneset, design = design_matrix_inter, contrast = contrast_matrix_interCD[,"CDvNon_CD"])
INFvNINF_camera_c2 <- camera(rld_entrez, index = geneset, design = design_matrix_intra, contrast = contrast_matrix_intraCD[,"INFvNINF"])
STENvNINF_camera_c2 <- camera(rld_entrez, index = geneset, design = design_matrix_intra, contrast = contrast_matrix_intraCD[,"STENvNINF"])

CDvNon_CD_camera_up <- CDvNon_CD_camera_c2[CDvNon_CD_camera_c2$Direction == "Up",]
CDvNon_CD_camera_down <- CDvNon_CD_camera_c2[CDvNon_CD_camera_c2$Direction == "Down",]
CDvNon_CD_up_plot <- pathway_enrichplot(CDvNon_CD_camera_up)
CDvNon_CD_down_plot <- pathway_enrichplot(CDvNon_CD_camera_down)

INFvNINF_camera_up <- INFvNINF_camera_c2[INFvNINF_camera_c2$Direction == "Up",]
INFvNINF_camera_down <- INFvNINF_camera_c2[INFvNINF_camera_c2$Direction == "Down",]
INFvNINF_up_plot <- pathway_enrichplot(INFvNINF_camera_up)
INFvNINF_down_plot <- pathway_enrichplot(INFvNINF_camera_down)

STENvNINF_camera_up <- STENvNINF_camera_c2[STENvNINF_camera_c2$Direction == "Up",]
STENvNINF_camera_down <- STENvNINF_camera_c2[STENvNINF_camera_c2$Direction == "Down",]
STENvNINF_up_plot <- pathway_enrichplot(STENvNINF_camera_up)
STENvNINF_down_plot <- pathway_enrichplot(STENvNINF_camera_down)
```

```{r STENvNINF: ECM pathways}
STENvNINF_camera_c2[grep("ECM", rownames(STENvNINF_camera_c2)),]

Cairo(file = file.path(STENvNINF_dir, "ECM_RECEPTOR_INTERACTION_barcode.pdf"), type = "pdf", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
barcodeplot(statistics = results_STENvNINF$stat, 
            index = which(results_STENvNINF$entrez_id %in% geneset$"R-HSA-3000178 Homo sapiens: ECM proteoglycans"),
            xlab = "Wald statistic",
            main = "ECM receptor interaction")
dev.off()

barcodeplot(statistics = results_STENvNINF$stat, 
            index = which(results_STENvNINF$entrez_id %in% msigdb_c2$REACTOME_MUSCLE_CONTRACTION),
            xlab = "stat")
```

Data for the manuscript
```{r Manuscript data}
manuscript_dir <- file.path("manuscript")
figure_dir <- file.path(manuscript_dir, "figures")
table_dir <- file.path(manuscript_dir, "tables")

#Figure 3 Enrichment DEGs
figure_deg_enrichment_dir <- file.path(figure_dir, "figure_3_DEG_enrichment")
dir.create(figure_deg_enrichment_dir)

Cairo(file = file.path(figure_deg_enrichment_dir, "CDvNon_CD_up_enrichment.pdf"), type = "pdf", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
print(CDvNon_CD_up_plot)
dev.off()
Cairo(file = file.path(figure_deg_enrichment_dir, "CDvNon_CD_down_enrichment.pdf"), type = "pdf", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
print(CDvNon_CD_down_plot)
dev.off()

Cairo(file = file.path(figure_deg_enrichment_dir, "STENvNINF_up_enrichment.pdf"), type = "pdf", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
print(STENvNINF_up_plot)
dev.off()
Cairo(file = file.path(figure_deg_enrichment_dir, "STENvNINF_down_enrichment.pdf"), type = "pdf", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
print(STENvNINF_down_plot)
dev.off()

Cairo(file = file.path(figure_deg_enrichment_dir, "ECM_proteoglycans.pdf"), type = "pdf", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
barcodeplot(statistics = results_STENvNINF$stat, 
            index = which(results_STENvNINF$entrez_id %in% geneset$"R-HSA-3000178 Homo sapiens: ECM proteoglycans"),
            xlab = "Wald statistic",
            main = "ECM proteoglycans")
dev.off()

Cairo(file = file.path(figure_deg_enrichment_dir, "Extracellular_matrix_organization.pdf"), type = "pdf", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
barcodeplot(statistics = results_STENvNINF$stat, 
            index = which(results_STENvNINF$entrez_id %in% geneset$"R-HSA-1474244 Homo sapiens: Extracellular matrix organization"),
            xlab = "Wald statistic",
            main = "ECM organization")
dev.off()

Cairo(file = file.path(figure_deg_enrichment_dir, "Elastic_fibre_formation.pdf"), type = "pdf", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
barcodeplot(statistics = results_STENvNINF$stat, 
            index = which(results_STENvNINF$entrez_id %in% geneset$"R-HSA-1566948 Homo sapiens: Elastic fibre formation"),
            xlab = "Wald statistic",
            main = "Elastic fiber formation")
dev.off()

Cairo(file = file.path(figure_deg_enrichment_dir, "Molecules_associated_with_elastic_fibres"), type = "pdf", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
barcodeplot(statistics = results_STENvNINF$stat, 
            index = which(results_STENvNINF$entrez_id %in% geneset$"R-HSA-2129379 Homo sapiens: Molecules associated with elastic fibres"),
            xlab = "Wald statistic",
            main = "Molecular associated with elastic fibers")
dev.off()

#Figure S3 Volcano plot
figure_deg_volcano_dir <- file.path(figure_dir, "figure_S3_DEG_volcanoplots")
dir.create(figure_deg_volcano_dir)

Cairo(file = file.path(figure_deg_volcano_dir, "CDvNon_CD_volcano.png"), type = "png", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
volcano_plot(effect_sizes = results_CDvNon_CD$log2FoldChange, 
             title = "CD vs non-CD",
             pvals = results_CDvNon_CD$pvalue, 
             significance = results_CDvNon_CD$padj < 0.05, 
             identifiers = results_CDvNon_CD$hgnc_symbol, 
             int_effect_threshold = 1, 
             top_names = 10)
dev.off()

Cairo(file = file.path(figure_deg_volcano_dir, "INFvNINF_volcano.png"), type = "png", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
volcano_plot(effect_sizes = results_INFvNINF$log2FoldChange, 
             title = "INF vs NINF",
             pvals = results_INFvNINF$pvalue, 
             significance = results_INFvNINF$padj < 0.05, 
             identifiers = results_INFvNINF$hgnc_symbol, 
             int_effect_threshold = 1, 
             top_names = 10)
dev.off()

Cairo(file = file.path(figure_deg_volcano_dir, "STENvNINF_volcano.png"), type = "png", units = "px", width = 800, height = 800, dpi = 90, bg = "white")
volcano_plot(effect_sizes = results_STENvNINF$log2FoldChange, 
             title = "STEN vs NINF",
             pvals = results_STENvNINF$pvalue, 
             significance = results_STENvNINF$padj < 0.05, 
             identifiers = results_STENvNINF$hgnc_symbol, 
             int_effect_threshold = 1, 
             top_names = 10)
dev.off()

#Table S4 DEGs
table_degs_dir <- file.path(table_dir, "table_s4_DEGs")
dir.create(table_degs_dir)

CDvNon_CD_DEGs_table <- data.frame(results_CDvNon_CD[, c("log2FoldChange", "lfcSE", "stat", "pvalue", "padj", "hgnc_symbol", "entrez_id")], rownames(results_CDvNon_CD))
INFvNINF_DEGs_table <- data.frame(results_INFvNINF[, c("log2FoldChange", "lfcSE", "stat", "pvalue", "padj", "hgnc_symbol", "entrez_id")], rownames(results_INFvNINF))
STENvNINF_DEGs_table <- data.frame(results_STENvNINF[, c("log2FoldChange", "lfcSE", "stat", "pvalue", "padj", "hgnc_symbol", "entrez_id")], rownames(results_STENvNINF))

colnames(STENvNINF_DEGs_table) <- colnames(INFvNINF_DEGs_table) <- colnames(CDvNon_CD_DEGs_table) <- c("Log2FC", "Log2FC-SE", "Wald", "pvalue", "padj", "Gene", "Entrez", "Ensembl")

deg_table <- list(CDvNon_CD = CDvNon_CD_DEGs_table,
                  INFvNINF = INFvNINF_DEGs_table,
                  STENvNINF = STENvNINF_DEGs_table)

require(openxlsx)
wb <- createWorkbook()
Map(function(data, name){
 
    addWorksheet(wb, name)
    writeData(wb, name, data)
 
}, deg_table, names(deg_table))

saveWorkbook(wb, file = file.path(table_degs_dir, "DEGs.xlsx"), overwrite = TRUE)

# Table S5 DEG enrichment
table_deg_enrichment_dir <- file.path(table_dir, "table_s5_DEG_enrichment")
dir.create(table_deg_enrichment_dir)

CDvNon_CD_ID <- gsub("(.+?) .+", "\\1", rownames(CDvNon_CD_camera_c2))
CDvNon_CD_DB <- rep("Reactome", nrow(CDvNon_CD_camera_c2))
CDvNon_CD_DB[grep("^hsa", CDvNon_CD_ID)] <- "KEGG"
CDvNon_CD_Desc <- gsub("^.+: (.+)$", "\\1", rownames(CDvNon_CD_camera_c2))

table_c2_CDvNon_CD <- data.frame(Database = CDvNon_CD_DB,
                                 Geneset_ID = CDvNon_CD_ID, 
                                 Description = CDvNon_CD_Desc, 
                                 pvalue = CDvNon_CD_camera_c2$PValue,
                                 padj = CDvNon_CD_camera_c2$FDR,
                                 Direction = CDvNon_CD_camera_c2$Direction,
                                 N_background = CDvNon_CD_camera_c2$NGenes)

INFvNINF_ID <- gsub("(.+?) .+", "\\1", rownames(INFvNINF_camera_c2))
INFvNINF_DB <- rep("Reactome", nrow(INFvNINF_camera_c2))
INFvNINF_DB[grep("^hsa", INFvNINF_ID)] <- "KEGG"
INFvNINF_Desc <- gsub("^.+: (.+)$", "\\1", rownames(INFvNINF_camera_c2))

table_c2_INFvNINF <- data.frame(Database = INFvNINF_DB,
                                 Geneset_ID = INFvNINF_ID, 
                                 Description = INFvNINF_Desc, 
                                 pvalue = INFvNINF_camera_c2$PValue,
                                 padj = INFvNINF_camera_c2$FDR,
                                 Direction = INFvNINF_camera_c2$Direction,
                                 N_background = INFvNINF_camera_c2$NGenes)

STENvNINF_camera_c2
STENvNINF_ID <- gsub("(.+?) .+", "\\1", rownames(STENvNINF_camera_c2))
STENvNINF_DB <- rep("Reactome", nrow(STENvNINF_camera_c2))
STENvNINF_DB[grep("^hsa", STENvNINF_ID)] <- "KEGG Pathways"
STENvNINF_Desc <- gsub("^.+: (.+)$", "\\1", rownames(STENvNINF_camera_c2))

table_c2_STENvNINF <- data.frame(Database = STENvNINF_DB,
                                 Geneset_ID = STENvNINF_ID, 
                                 Description = STENvNINF_Desc, 
                                 pvalue = STENvNINF_camera_c2$PValue,
                                 padj = STENvNINF_camera_c2$FDR,
                                 Direction = STENvNINF_camera_c2$Direction,
                                 N_background = STENvNINF_camera_c2$NGenes)

tables_DEG_enrichment <- list(CDvNon_CD = table_c2_CDvNon_CD,
                              STENvNINF = table_c2_STENvNINF)

require(openxlsx)
wb <- createWorkbook()
Map(function(data, name){
 
    addWorksheet(wb, name)
    writeData(wb, name, data)
 
}, tables_DEG_enrichment, names(tables_DEG_enrichment))

saveWorkbook(wb, file = file.path(table_deg_enrichment_dir, "DEG_pathway_enrichment.xlsx"), overwrite = TRUE)
```

```{r Final}
sessionInfo()
today <- gsub("^([0-9]{4})-([0-9]{2})-([0-9]{2}).+$", "\\1\\2\\3", Sys.time())

rdata_dir <- file.path(output_dir, "rdata")
dir.create(rdata_dir)
save.image(file = file.path(output_dir, "rdata", paste0(today, ".RData")))
```